---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {sudokur}

<!-- badges: start -->
<!-- badges: end -->

This package is designed to solve any 9 by 9 sudoku grid using the backtracking algorithm.

## Installation

You can install the development version of sudokur from [GitHub](https://github.com/) with:

```{r include=FALSE}
devtools::load_all('.')
```


``` r
# install.packages("devtools")
devtools::install_github("kennedymwavu/sudokur")
```

## Usage

### Include your own sudoku grids

To make your own customized sudoku puzzle which you can view and solve with the functions available in this package, create a 9 by 9 matrix with zeros representing the empty spaces in your sudoku.

Example:

```{r}
board1 <- matrix(
  data = c(
    5, 6, 0, 8, 4, 7, 0, 0, 0,
    3, 0, 9, 0, 0, 0, 6, 0, 0,
    0, 0, 8, 0, 0, 0, 0, 0, 0,
    0, 1, 0, 0, 8, 0, 0, 4, 0,
    7, 9, 0, 6, 0, 2, 0, 1, 8,
    0, 5, 0, 0, 3, 0, 0, 9, 0,
    0, 0, 0, 0, 0, 0, 2, 0, 0,
    0, 0, 6, 0, 0, 0, 8, 0, 7,
    0, 0, 0, 3, 1, 6, 0, 5, 9
    ),
  ncol = 9
)
```

### Pretty print a sudoku grid

To pretty print a sudoku grid use `print_board(given_board)`.

Example:

```{r}
print_board(board1)
```


### Solve sudoku puzzles

To solve a sudoku puzzle `solve_sudoku(given_board)`.

Example:

```{r}
solve_sudoku(samples$board6)
```

